---
title: "Schedule"
slug: schedule
summary: "Schedule of the Gov 2002 semester with readings, due dates, and links to materials."
toc: false
sidebar: false
page-layout: full
---
                     
```{r packages-data, include=FALSE} 
library(tidyverse)
library(knitr)
library(kableExtra)
library(lubridate)
library(glue)

schedule <- read_csv("data/schedule.csv", show_col_types = FALSE) 
```
   
Below is the schedule for the semester. You can find the materials for each course meeting under the “Content” links for that week. You should generally complete the reading before attending lecture. Here's a guide to the schedule:        

- [**Materials**](/materials/) ({{< fa book-open-reader >}}): This page contains the readings, slides, and recorded lectures (if any) for the topic. Read/watch these first.
- **Assignment** ({{< fa pen-ruler >}}): This page contains the instructions for each assignment. **Assignments are due by 11:59 PM on the day they're listed.**

The readings refer to following texts:

- BH: Blitzstein and Hwang, [*Introduction to Probability, Second Edition*](https://projects.iq.harvard.edu/stat110/home).
- UG: Blackwell, [*A User's Guide to Statistical Inference and Regression*](https://mattblackwell.github.io/gov2002-book/)
- HE: Hansen, [*Econometrics*](https://www.ssc.wisc.edu/~bhansen/econometrics/Econometrics.pdf).

The BH and UG readings are the ones that we will focus on, but I have also included references for Hansen in case you have that book and want to see a different or more technical discussion of the material.         
 
     
```{r build-table, echo=FALSE, results="asis"}
schedule <- schedule %>%  
    mutate(var_title = ifelse(!is.na(content),
                              glue('<span class="content-title">{title}</span>'),
                              glue('{title}'))) %>%
  mutate(var_reading = ifelse(!is.na(reading),
                              glue('<span class="content-reading">{reading}</span>'),
                              glue(""))) %>%
    mutate(var_deadline = ifelse(!is.na(deadline),
                                 glue('&emsp;&emsp;<small>(submit by {deadline})</small>'),
                                 glue(""))) %>%
    mutate(var_content = ifelse(!is.na(content),
                                glue('<a href="{content}.qmd"><i class="fa-solid fa-book-open-reader fa-lg"></i></a>'),
                                glue('<font color="#e9ecef"><i class="fa-solid fa-book-open-reader fa-lg"></i></font>'))) %>%
    mutate(var_assignment = ifelse(!is.na(assignment),
                                   glue('<a href="{assignment}.qmd"><i class="fa-solid fa-pen-ruler fa-lg"></i></a>'),
                                   glue('<font color="#e9ecef"><i class="fa-solid fa-pen-ruler fa-lg"></i></font>'))) %>%
    mutate(col_date = ifelse(is.na(date_end),
                             glue('<strong>{format(date, "%B %e")}</strong>'),
                             glue('<strong>{format(date, "%B %e")}</strong>–<strong>{format(date_end, "%B %e")}</strong>'))) %>%
    mutate(col_title = glue('{var_title}{var_deadline}')) %>%
    mutate(col_content = var_content,
           col_reading = var_reading,
           col_assignment = var_assignment) %>%
  select(Week = week, Date = col_date, Title = col_title, Reading = col_reading, Materials = col_content, Assignment = col_assignment) 

week_count <- schedule |> count(Week)
week_index <- week_count |> pull(n) |> set_names(paste0("Week ", week_count$Week))
 
tbl <- schedule |>
  select(-Week) |>
  kbl(escap = FALSE, align = "rllccccc", table.attr = 'class="schedule-table"') |>
  kable_styling() |>
  column_spec(1, width = "20%", extra_css = "padding-right: 20px;") |>  
  column_spec(2, width = "45%") |>  
  column_spec(3, width = "20%") |>  
  column_spec(c(4:5), width = "5%") |>
  pack_rows(index = week_index,
              label_row_css = "border-bottom: 2px solid #000000;")

  cat(tbl)
```
  
